Toxic Code Snippets on Stack Overflow

### 2019-02-16 cloverflow-tse/submitted_version/16-Feb-2019_final_files_for_submission/cloverflow.tex
Added the modified version of the source files. TSE requires some specific file format for images (must be eps, ps, tiff, ppt, or png).

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{cragkhit.jpg}}]{Chaiyong Ragkhitwetsagul}
is a lecturer at the Faculty of Information and Communication Technology, Mahidol University, Thailand. He received the PhD degree in Computer Science at University College London, where he was part of the Centre for Research on Evolution, Search, and Testing (CREST). His research interests include code search, code clone detection, software plagiarism, modern code review, and mining software repositories. %More info: \url{http://mucc.mahidol.ac.th/~chaiyong.rag}.
\end{IEEEbiography}
%\vspace{-1cm}

% % if you will not have a photo at all:
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{jkrinke.jpg}}]{Jens Krinke}
is Associate Professor in the Software Systems Engineering
Group at the University College London, where he is Director of CREST,
the Centre for Research on Evolution, Search, and Testing.  His main
focus is software analysis for software engineering purposes. His
current research interests include software
similarity, modern code review, program analysis, and software testing.  He is well known for his work on
program slicing and clone detection.
\end{IEEEbiography}
%\vspace{-1cm}

>>>>

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{cragkhit.png}}]{Chaiyong Ragkhitwetsagul}
is a lecturer at the Faculty of Information and Communication Technology, Mahidol University, Thailand. He received the PhD degree in Computer Science at University College London, where he was part of the Centre for Research on Evolution, Search, and Testing (CREST). His research interests include code search, code clone detection, software plagiarism, modern code review, and mining software repositories. %More info: \url{http://mucc.mahidol.ac.th/~chaiyong.rag}.
\end{IEEEbiography}
%\vspace{-1cm}

% % if you will not have a photo at all:
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{jkrinke.png}}]{Jens Krinke}
is Associate Professor in the Software Systems Engineering
Group at the University College London, where he is Director of CREST,
the Centre for Research on Evolution, Search, and Testing.  His main
focus is software analysis for software engineering purposes. His
current research interests include software
similarity, modern code review, program analysis, and software testing.  He is well known for his work on
program slicing and clone detection.
\end{IEEEbiography}
%\vspace{-1cm}
